---
title: "Analysis of Gene Signatures in DE Results"
author: "Theo Killian"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, echo = FALSE, results = 'asis'}
# Set global knitr options
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  warning  = FALSE,
  message  = FALSE
)

# Load required packages
suppressPackageStartupMessages({
  library(dplyr)
  library(tidyr)
  library(tibble)
  library(stringr)
  library(ggplot2)
  library(ggrepel)
  library(knitr)
  library(RColorBrewer)
  library(readxl)
  library(writexl)
  library(org.Mm.eg.db)
  library(clusterProfiler)
  library(fgsea)
  library(DOSE)
  library(DT)
})

# set project name
project_name <- "karthik_mice_obesity"

# Set seed for reproducibility
set.seed(123)
```

# Introduction

In order to understand the underlying biology of the DE genes generated from the
earlier DESeq2 report, we will be comparing the significant DE genes to select
gene signatures taken from the supplementary material found in
[Karras, et al 2022](https://www.nature.com/articles/s41586-022-05242-7#Sec50).
This report will generate volcano plots to visualize the expression of the 
melanoma gene signature genes, annotate the DE gene list with the melanoma gene
signatures and perform custom GSEA to rank the enrichment of melanoma gene
signature genes within the DE results using [fgsea](https://www.bioconductor.org/packages/devel/bioc/vignettes/fgsea/inst/doc/fgsea-tutorial.html).

## Read Signature File

The supplementary file containing DE gene lists on sheet 3 of the Excel file from
[Karras, et al 2022](https://www.nature.com/articles/s41586-022-05242-7#Sec50)
is read below: 

<!-- ```{r} -->
<!-- readxl::read_excel("./data/41586_2022_5242_MOESM3_ESM.xlsx", -->
<!--                    sheet = 1, -->
<!--                    skip = 2) %>% -->
<!--   dplyr::rename(gene_symbol = names(.)[1]) %>% -->
<!--   dplyr::select(-gene) %>% -->
<!--   # dplyr::mutate(signature_type = dplyr::case_when( -->
<!--   #   cluster == 0 ~ "" -->
<!--   #   # Stem-like	Neural Crest-like	Mesenchymal-like	RNA processing	Antigen Presentation	Stress-like (hypoxia) 	Melanocytic (Oxphos) -->
<!--   # )) -->
<!--   dplyr::filter(cluster == 4, -->
<!--                 avg_logFC > 1) %>% -->
<!--   as.data.frame() -> sig_sheet_1 -->
<!-- # View(sig_sheet_1) -->
<!-- ``` -->

```{r}
readxl::read_excel("./data/41586_2022_5242_MOESM3_ESM.xlsx",
                   sheet = 3,
                   skip = 2) %>%
  as.data.frame() -> sig_sheet_3

DT::datatable(sig_sheet_3)
```

## Annotate DE Genes with Melanoma Signature Genes

```{r warning=FALSE, message=FALSE}
res_data <- readRDS("./results/karthik_mice_obesity_DE_results_2025-05-18.rds")

sig_sheet_3 %>% 
  tidyr::pivot_longer(
    cols = everything(),
    names_to = "signature",
    values_to = "gene_name") %>%
  dplyr::filter(!is.na(gene_name)) %>%
  as.data.frame() -> sig_list_long

res_data %>%
  dplyr::filter(!is.na(pvalue)) %>%
  dplyr::mutate(
    negLogP = -log10(pvalue),
    sig = ifelse(padj < 0.05 & abs(log2FoldChange) > 1,
                 "Significant", "Not Significant")) %>%
  dplyr::left_join(sig_list_long, by = "gene_name") %>%
  as.data.frame() -> res_data_annotated

res_data_annotated %>%
  dplyr::select(-c(contains("_rep"), contains("_id"), lfcSE, stat, sig, negLogP)) %>%
  dplyr::mutate(
    log2FoldChange = round(log2FoldChange, 3),
    baseMean       = round(baseMean, 1),
    pvalue         = signif(pvalue, 3),
    padj           = signif(padj, 3)) %>%
  dplyr::select(gene_name, signature, everything()) %>%
  as.data.frame() -> res_data_annotated_table

res_data_annotated_table %>%
  dplyr::filter(stringr::str_length(signature) > 1) %>%
  DT::datatable(
    options = list(pageLength = 10),
    caption = "Annotated Differential Expression Results of Melanoma Signature Genes: ")
```

**Of all the genes in the signature lists, only 3 genes in the "Mesenchymal-like" gene list appear in the significant results, and all of them are higher in the "IgG" condition.**

```{r}
res_data_annotated_table %>%
  dplyr::filter(padj < 0.05,
                stringr::str_length(signature) > 1) %>%
  DT::datatable()
```

## GSEA With ClusterProfiler Using Defined Melanoma Signatures 

We use the [fgsea](https://www.bioconductor.org/packages/devel/bioc/vignettes/fgsea/inst/doc/fgsea-tutorial.html)
R package to perform GSEA on our custom melanoma signatures taken from the 
supplementary tables in Karras, et al 2022.

```{r warning=FALSE, message=FALSE}
mouse_biomart <- readRDS(file = "./data/mouse_biomart.rds")
sig_list_long %>%
  dplyr::left_join(mouse_biomart, by = "gene_name") %>% 
  dplyr::filter(!is.na(gene_name),
                !is.na(entrez_id)) %>%
  dplyr::select(-ensembl_id) %>%
  dplyr::rename(SYMBOL = gene_name,
                ENTREZID = entrez_id) %>%
  as.data.frame() -> entrez_genes

readRDS(file = "./results/karthik_mice_obesity_DE_results_2025-05-18.rds") %>%
  dplyr::filter(
    !is.na(gene_name),
    !is.na(entrez_id),
    !duplicated(gene_name),
    !duplicated(entrez_id),
    !is.na(log2FoldChange),
    !is.na(pvalue)) %>%
  dplyr::arrange(desc(stat)) %>%
  dplyr::select(entrez_id, stat) %>%
  dplyr::rename(ENTREZID = entrez_id) %>%
  tibble::deframe() -> gene_list

list(
   entrez_genes %>% 
    dplyr::filter(signature == unique(entrez_genes$signature)[1]) %>%
    dplyr::mutate(ENTREZID = as.character(ENTREZID)) %>%
    dplyr::pull(ENTREZID),
  entrez_genes %>% 
    dplyr::filter(signature == unique(entrez_genes$signature)[2]) %>%
    dplyr::mutate(ENTREZID = as.character(ENTREZID)) %>%
    dplyr::pull(ENTREZID),
  entrez_genes %>% 
    dplyr::filter(signature == unique(entrez_genes$signature)[3]) %>%
    dplyr::mutate(ENTREZID = as.character(ENTREZID)) %>%
    dplyr::pull(ENTREZID),
  entrez_genes %>% 
    dplyr::filter(signature == unique(entrez_genes$signature)[4]) %>%
    dplyr::mutate(ENTREZID = as.character(ENTREZID)) %>%
    dplyr::pull(ENTREZID),
  entrez_genes %>% 
    dplyr::filter(signature == unique(entrez_genes$signature)[5]) %>%
    dplyr::mutate(ENTREZID = as.character(ENTREZID)) %>%
    dplyr::pull(ENTREZID),
  entrez_genes %>% 
    dplyr::filter(signature == unique(entrez_genes$signature)[6]) %>%
    dplyr::mutate(ENTREZID = as.character(ENTREZID)) %>%
    dplyr::pull(ENTREZID),
  entrez_genes %>% 
    dplyr::filter(signature == unique(entrez_genes$signature)[7]) %>%
    dplyr::mutate(ENTREZID = as.character(ENTREZID)) %>%
    dplyr::pull(ENTREZID)) %>%
  setNames(unique(entrez_genes$signature)) -> melanoma_gene_sets

fgsea::fgsea(
  pathways = melanoma_gene_sets,
  stats = gene_list) %>% 
  dplyr::arrange(padj) -> melanoma_gsea_res

melanoma_gsea_res %>%
  dplyr::mutate(
    log2err = round(log2err, 3),
    ES       = round(ES, 3),
    NES       = round(NES, 3),
    pval         = signif(pval, 3),
    padj           = signif(padj, 3)) %>%
  dplyr::select(-leadingEdge) %>%
  DT::datatable()
```

```{r}
plotGseaTable(melanoma_gene_sets, gene_list, melanoma_gsea_res, 
              gseaParam=0.5)
```

## Volcano Plots

We will be visualizing the following gene signatures shown below in volcano
plots to visually illustrate what the genes in these melanoma signature gene sets
are expressing with respect to each condition.

<!-- ```{r} -->
<!-- names(sig_sheet_3) %>% -->
<!--   as.data.frame() %>%  -->
<!--   dplyr::rename(Signatures = names(.)[1]) %>%  -->
<!--   knitr::kable() -->
<!-- ``` -->

### Standard Volcano Plot

A Volcano plot (log2 fold change vs -log10 p-value) helps identify genes that
display large magnitude changes and high significance.

**NOTE: This is the same volcano plot from the previous DE analysis; it is displayed here purely for reference!**

```{r}
res_data %>%
  dplyr::filter(!is.na(pvalue)) %>%
  dplyr::mutate(
    negLogP = -log10(pvalue),
    sig = ifelse(padj < 0.05 & abs(log2FoldChange) > 1,
                 "Significant", "Not Significant")) -> volcano_data
volcano_data %>%
  ggplot(aes(x = log2FoldChange, y = negLogP, color = sig)) +
  geom_point(size = 0.75, alpha = 0.75) +
  geom_text_repel(data = subset(volcano_data, sig == "Significant"),
                  aes(label = gene_name), size = 3, max.overlaps = Inf,
                  box.padding = 0.3, point.padding = 0.3, segment.color = "grey50") +
  scale_color_manual(values = c("Significant" = "red", "Not Significant" = "black")) +
  geom_hline(yintercept = -log10(0.05), color = "blue", linetype = "dashed") +
  geom_vline(xintercept = c(-1, 1), color = "blue", linetype = "dashed") +
  theme_bw() +
  ggtitle("Volcano Plot")
```

### Volcano Plot Highlighting "Stem-like" Genes

```{r}
sig_sheet_3 %>% 
  dplyr::filter(!is.na(`Stem-like`)) %>%
  dplyr::pull(`Stem-like`) -> sig_list1

res_data %>%
  dplyr::filter(!is.na(pvalue)) %>%
  dplyr::mutate(
    negLogP = -log10(pvalue),
    sig = ifelse(padj < 0.05 & abs(log2FoldChange) > 1,
                 "Significant", "Not Significant"),
    is_target = ifelse(gene_name %in% sig_list1, "Target", "Other")) %>%
  as.data.frame() -> volcano_data

ggplot(volcano_data, aes(x = log2FoldChange, y = negLogP)) +
  geom_point(aes(color = is_target), size = 0.75, alpha = 0.75) +
  scale_color_manual(values = c("Target" = "green3", "Other" = "black")) +
  geom_text_repel(
    data = subset(volcano_data, is_target == "Target"),
    aes(label = gene_name),
    size = 3,
    max.overlaps = Inf,
    box.padding = 0.3,
    point.padding = 0.3,
    segment.color = "grey50",
    color = "green3") +
  geom_hline(yintercept = -log10(0.05), color = "blue", linetype = "dashed") +
  geom_vline(xintercept = c(-1, 1), color = "blue", linetype = "dashed") +
  theme_bw() +
  ggtitle(paste0("Volcano Plot Highlighting ", names(sig_sheet_3)[1], " Genes"))
```

### Volcano Plot Highlighting "Neural Crest-like" Genes

```{r warning=FALSE, message=FALSE}
sig_sheet_3 %>% 
  dplyr::filter(!is.na(`Mesenchymal-like`)) %>%
  dplyr::pull(`Neural Crest-like`) -> sig_list2

res_data %>%
  dplyr::filter(!is.na(pvalue)) %>%
  dplyr::mutate(
    negLogP = -log10(pvalue),
    sig = ifelse(padj < 0.05 & abs(log2FoldChange) > 1,
                 "Significant", "Not Significant"),
    is_target = ifelse(gene_name %in% sig_list2, "Target", "Other")) %>%
  as.data.frame() -> volcano_data

ggplot(volcano_data, aes(x = log2FoldChange, y = negLogP)) +
  geom_point(aes(color = is_target), size = 0.75, alpha = 0.75) +
  scale_color_manual(values = c("Target" = "mistyrose4", "Other" = "black")) +
  geom_text_repel(
    data = subset(volcano_data, is_target == "Target"),
    aes(label = gene_name),
    size = 3,
    max.overlaps = Inf,
    box.padding = 0.3,
    point.padding = 0.3,
    segment.color = "grey50",
    color = "mistyrose4") +
  geom_hline(yintercept = -log10(0.05), color = "blue", linetype = "dashed") +
  geom_vline(xintercept = c(-1, 1), color = "blue", linetype = "dashed") +
  theme_bw() +
  ggtitle(paste0("Volcano Plot Highlighting ", names(sig_sheet_3)[2], " Genes"))
```

### Volcano Plot Highlighting "Mesenchymal-like" Genes

```{r}
sig_sheet_3 %>% 
  dplyr::filter(!is.na(`Mesenchymal-like`)) %>%
  dplyr::pull(`Mesenchymal-like`) -> sig_list3

res_data %>%
  dplyr::filter(!is.na(pvalue)) %>%
  dplyr::mutate(
    negLogP = -log10(pvalue),
    sig = ifelse(padj < 0.05 & abs(log2FoldChange) > 1,
                 "Significant", "Not Significant"),
    is_target = ifelse(gene_name %in% sig_list3, "Target", "Other")) %>%
  as.data.frame() -> volcano_data

ggplot(volcano_data, aes(x = log2FoldChange, y = negLogP)) +
  geom_point(aes(color = is_target), size = 0.75, alpha = 0.75) +
  scale_color_manual(values = c("Target" = "hotpink4", "Other" = "black")) +
  geom_text_repel(
    data = subset(volcano_data, is_target == "Target"),
    aes(label = gene_name),
    size = 3,
    max.overlaps = Inf,
    box.padding = 0.3,
    point.padding = 0.3,
    segment.color = "grey50",
    color = "hotpink4") +
  geom_hline(yintercept = -log10(0.05), color = "blue", linetype = "dashed") +
  geom_vline(xintercept = c(-1, 1), color = "blue", linetype = "dashed") +
  theme_bw() +
  ggtitle(paste0("Volcano Plot Highlighting ", names(sig_sheet_3)[3], " Genes"))
```

### Volcano Plot Highlighting "RNA processing" Genes

```{r}
sig_sheet_3 %>% 
  dplyr::filter(!is.na(`RNA processing`)) %>%
  dplyr::pull(`RNA processing`) -> sig_list4

res_data %>%
  dplyr::filter(!is.na(pvalue)) %>%
  dplyr::mutate(
    negLogP = -log10(pvalue),
    sig = ifelse(padj < 0.05 & abs(log2FoldChange) > 1,
                 "Significant", "Not Significant"),
    is_target = ifelse(gene_name %in% sig_list4, "Target", "Other")) %>%
  as.data.frame() -> volcano_data

ggplot(volcano_data, aes(x = log2FoldChange, y = negLogP)) +
  geom_point(aes(color = is_target), size = 0.75, alpha = 0.75) +
  scale_color_manual(values = c("Target" = "#008B8B", "Other" = "black")) +
  geom_text_repel(
    data = subset(volcano_data, is_target == "Target"),
    aes(label = gene_name),
    size = 3,
    max.overlaps = Inf,
    box.padding = 0.3,
    point.padding = 0.3,
    segment.color = "grey50",
    color = "#008B8B") +
  geom_hline(yintercept = -log10(0.05), color = "blue", linetype = "dashed") +
  geom_vline(xintercept = c(-1, 1), color = "blue", linetype = "dashed") +
  theme_bw() +
  ggtitle(paste0("Volcano Plot Highlighting ", names(sig_sheet_3)[4], " Genes"))
```

### Volcano Plot Highlighting "Antigen Presentation" Genes

```{r}
sig_sheet_3 %>% 
  dplyr::filter(!is.na(`Antigen Presentation`)) %>%
  dplyr::pull(`Antigen Presentation`) -> sig_list5

res_data %>%
  dplyr::filter(!is.na(pvalue)) %>%
  dplyr::mutate(
    negLogP = -log10(pvalue),
    sig = ifelse(padj < 0.05 & abs(log2FoldChange) > 1,
                 "Significant", "Not Significant"),
    is_target = ifelse(gene_name %in% sig_list5, "Target", "Other")) %>%
  as.data.frame() -> volcano_data

ggplot(volcano_data, aes(x = log2FoldChange, y = negLogP)) +
  geom_point(aes(color = is_target), size = 0.75, alpha = 0.75) +
  scale_color_manual(values = c("Target" = "#C71585", "Other" = "black")) +
  geom_text_repel(
    data = subset(volcano_data, is_target == "Target"),
    aes(label = gene_name),
    size = 3,
    max.overlaps = Inf,
    box.padding = 0.3,
    point.padding = 0.3,
    segment.color = "grey50",
    color = "#C71585") +
  geom_hline(yintercept = -log10(0.05), color = "blue", linetype = "dashed") +
  geom_vline(xintercept = c(-1, 1), color = "blue", linetype = "dashed") +
  theme_bw() +
  ggtitle(paste0("Volcano Plot Highlighting ", names(sig_sheet_3)[5], " Genes"))
```

### Volcano Plot Highlighting "Stress-like (hypoxia)" Genes

```{r}
sig_sheet_3 %>% 
  dplyr::filter(!is.na(`Stem-like`)) %>%
  dplyr::pull(`Stem-like`) -> sig_list6

res_data %>%
  dplyr::filter(!is.na(pvalue)) %>%
  dplyr::mutate(
    negLogP = -log10(pvalue),
    sig = ifelse(padj < 0.05 & abs(log2FoldChange) > 1,
                 "Significant", "Not Significant"),
    is_target = ifelse(gene_name %in% sig_list6, "Target", "Other")) %>%
  as.data.frame() -> volcano_data

ggplot(volcano_data, aes(x = log2FoldChange, y = negLogP)) +
  geom_point(aes(color = is_target), size = 0.75, alpha = 0.75) +
  scale_color_manual(values = c("Target" = "#B22222", "Other" = "black")) +
  geom_text_repel(
    data = subset(volcano_data, is_target == "Target"),
    aes(label = gene_name),
    size = 3,
    max.overlaps = Inf,
    box.padding = 0.3,
    point.padding = 0.3,
    segment.color = "grey50",
    color = "#B22222") +
  geom_hline(yintercept = -log10(0.05), color = "blue", linetype = "dashed") +
  geom_vline(xintercept = c(-1, 1), color = "blue", linetype = "dashed") +
  theme_bw() +
  ggtitle(paste0("Volcano Plot Highlighting ", names(sig_sheet_3)[6], " Genes"))
```

### Volcano Plot Highlighting "Melanocytic (Oxphos)" Genes

```{r}
sig_sheet_3 %>% 
  dplyr::filter(!is.na(`Melanocytic (Oxphos)`)) %>%
  dplyr::pull(`Melanocytic (Oxphos)`) -> sig_list7

res_data %>%
  dplyr::filter(!is.na(pvalue)) %>%
  dplyr::mutate(
    negLogP = -log10(pvalue),
    sig = ifelse(padj < 0.05 & abs(log2FoldChange) > 1,
                 "Significant", "Not Significant"),
    is_target = ifelse(gene_name %in% sig_list7, "Target", "Other")) %>%
  as.data.frame() -> volcano_data

ggplot(volcano_data, aes(x = log2FoldChange, y = negLogP)) +
  geom_point(aes(color = is_target), size = 0.75, alpha = 0.75) +
  scale_color_manual(values = c("Target" = "sienna3", "Other" = "black")) +
  geom_text_repel(
    data = subset(volcano_data, is_target == "Target"),
    aes(label = gene_name),
    size = 3,
    max.overlaps = Inf,
    box.padding = 0.3,
    point.padding = 0.3,
    segment.color = "grey50",
    color = "sienna3") +
  geom_hline(yintercept = -log10(0.05), color = "blue", linetype = "dashed") +
  geom_vline(xintercept = c(-1, 1), color = "blue", linetype = "dashed") +
  theme_bw() +
  ggtitle(paste0("Volcano Plot Highlighting ", names(sig_sheet_3)[7], " Genes"))
```

<!-- ## Interpretation of DE Results -->

<!-- Experimental Design Hypothesis -->

<!--     "IgG" refers to an isotype control antibody, i.e., a negative control treatment. -->

<!--     "PD1" refers to  immune checkpoint blockade treatment with anti-PD-1 antibodies. -->

<!-- This setup suggests the experiment aims to model the effects of PD-1 blockade on tumor-bearing (or obesity-prone) mice, and observe how immune responses and metabolic pathways change. -->

<!-- Here, we group the differentially expressed genes by putative function or role: -->

<!-- A. Immune Checkpoint and T cell Exhaustion Markers -->

<!--     Pdcd1 (PD-1) – the target of the treatment. -->

<!--     Ctla4, Tigit, Tox, Il2rb, Bcl11b, Gimap7, Cd8a, Cd7, Nr4a2 – all associated with T cell differentiation, activation, and exhaustion. -->

<!--     Tox, Nr4a2, and Tigit are canonical markers of exhausted T cells (Tex), particularly in chronic infections and tumors. -->

<!--     Gimap7 is implicated in T cell survival and development. -->

<!--     Cd8a, Cd7 suggest cytotoxic T cell involvement. -->

<!--     Il2rb (CD122) is part of the IL-2/IL-15 signaling axis, important for effector T cell responses. -->

<!--   This strongly supports an immune context where anti-PD-1 therapy modulates T cell states. -->

<!-- B. Immunoglobulin and Antigen Presentation -->

<!--     Ighg2b – an immunoglobulin heavy chain, possibly indicating B cell activity or humoral immune response. -->

<!--     H2-M2 – an MHC class Ib gene involved in antigen presentation. -->

<!--   Suggests adaptive immune system remodeling post anti-PD-1 treatment. -->

<!-- C. Tumor and Stemness Markers -->

<!--     Sox2, Pou2f2 – transcription factors linked to pluripotency and stem-like phenotypes, often seen in cancer stem cells. -->

<!--     Krt19 – a cytokeratin linked to epithelial tumors and often used as a cancer biomarker. -->

<!--     Timp3 – a tissue inhibitor of metalloproteinases, often involved in ECM remodeling and metastasis. -->

<!--   Could reflect changes in tumor cell states or the tumor microenvironment under immune pressure. -->

<!-- D. ECM/Structural/Metabolic Genes -->

<!--     Fbn2, Col1a1, Eln, Slit3, Itga7, Timp3 – involved in extracellular matrix remodeling, which can be related to both tumor progression and adipose tissue remodeling in obesity. -->

<!--     Ccdc3 – a secreted factor enriched in adipocytes, with links to metabolism. -->

<!--     Ptpn22 – linked to autoimmunity and metabolic inflammation. -->

<!--     Cables1 – tumor suppressor roles and links to cell cycle control. -->

<!--     Lrp4 – part of Wnt signaling, important in metabolism and cancer. -->

<!--   These genes hint at cross-talk between immune activity, ECM remodeling, and metabolic state—consistent with obesity influencing tumor-immune interactions. -->


<!-- The DE gene list is highly coherent with the hypothesis that: -->

<!--     PD-1 blockade is modifying T cell exhaustion, enhancing cytotoxic responses. -->

<!--     There is tumor-related transcriptional plasticity, potentially affecting stemness and ECM interactions. -->

<!--     The interplay between cancer immunity and obesity/metabolism is present—perhaps via shared inflammatory or stromal pathways. -->

<!-- This would fit in with: -->

<!--     Mouse models of diet-induced obesity and cancer (e.g., breast or colon cancer), where obesity is known to dampen anti-PD-1 response. -->

<!--     The possibility that PD-1 therapy partially restores immune function even in metabolically altered environments. -->

## Saving Outputs

The results are saved as `.rds` and `.xlsx` files for downstream use:

```{r write_data, warning=FALSE, message=FALSE}
## save table of melanoma GSEA results
write_xlsx(x = melanoma_gsea_res,
           path = paste0("./results/", project_name, "_melanoma_signature_GSEA_results_",
                         Sys.Date(), ".xlsx"))

# Save DE result object
saveRDS(object = res_data_annotated,
        file = paste0("./results/", project_name, "_DE_results_annotated_",
                      Sys.Date(), ".rds"))

# Save an Excel file
write_xlsx(x = res_data_annotated,
           path = paste0("./results/", project_name, "_DE_results_annotated_",
                         Sys.Date(), ".xlsx"))
```

*Session Info*

```{r sessionInfo}
sessionInfo()
```